VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-07-18 snapshot_system/paper_intro.tex
full revision sweep

%Without deduplication,
Source-side deduplication (e.g. ~\cite{Symantec2009})
 eliminates duplicates before backup data is transmitted
to a secondary storage, which saves network bandwidth significantly; however its resource
usage can impact other co-located cloud services. 
But it is memory-intensive to compare a large number of fingerprints and identify
duplicates, even optimization or approximation techniques are developed~\cite{Guo2011,Dong2011,extreme_binning09}. 
When deleting unused snapshots, a mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  
is effective while it still carries a significant cost, especially in a distributed
setting.  Another side effect of deduplication is the possible loss of failure
resilience~\cite{Reliability06}.  Separate files share the same physical copies of blocks that are
logically duplicated among them.  If a shared block is lost, all files that
share that block are affected.  
A cloud may offload backup workload from production 
server hosts to dedicated backup proxy servers (e.g. EMC Data Domain) or
backup services (e.g. Amazon S3). This approach simplifies the cluster 
architecture and 
avoids potential performance degradation to production applications when 
backups are in progress.
However, sending out undeduplicated backup data wastes huge amount
of network bandwidth that would otherwise be available to user VMs. 
\comments{
Even when the storage system implements deduplication internally
such dedicated backup storage is either difficult to scale out
(which can comprise the overall scalability of the converged architecture) 
or it must forego global deduplication in order to gain scalability 
(which increases backup cost).
}

This paper considers a backup service for converged cloud architectures
that is co-located with user VMs, sharing the cloud computer, network, and
storage resource with them.  We propose a VM-centric approach that
simplifies deduplication and snapshot deletion.
The key advantage of this approach  is that while maintaining  a competitive deduplication efficiency,
the scheme uses a small resource usage without affecting other collocated cloud services.
\comments{
The key contribution of this work is a set of methodologies to address the following two challenges:
1) simple deduplication and snapshot deletion with competitive efficiency and 
a small resource usage without affecting other collocated cloud services;
2) improved fault isolation for the sharing of deduplicated data,
given that node failures in converged architecture are the norm rather than
exception.

>>>>

%Without deduplication,
Source-side deduplication (e.g. ~\cite{Symantec2009})
 eliminates duplicates before backup data is transmitted
to a secondary storage, which saves network bandwidth significantly; however its resource
usage can impact other co-located cloud services. 
But it is memory-intensive to compare a large number of fingerprints and identify
duplicates, even optimization or approximation techniques are developed~\cite{Guo2011,Dong2011,extreme_binning09}. 
When deleting unused snapshots, a mark-and-sweep approach~\cite{Guo2011,Fabiano2013}  
is effective while it still carries a significant cost, especially in a distributed
setting.  Another side effect of deduplication is the possible loss of failure
resilience~\cite{Reliability06}.  Separate files share the same physical copies of blocks that are
logically duplicated among them.  If a shared block is lost, all files that
share that block are affected.  
A cloud may offload backup workload from production 
server hosts to dedicated backup proxy servers (e.g. EMC Data Domain) or
backup services (e.g. Amazon S3). This approach simplifies the cluster 
architecture and 
avoids potential performance degradation to production applications when 
backups are in progress.
However, sending out undeduplicated backup data wastes a huge amount
of network bandwidth that would otherwise be available to user VMs. 
\comments{
Even when the storage system implements deduplication internally
such dedicated backup storage is either difficult to scale out
(which can comprise the overall scalability of the converged architecture) 
or it must forego global deduplication in order to gain scalability 
(which increases backup cost).
}

This paper considers a backup service for converged cloud architectures
that is co-located with user VMs, sharing the cloud compute, network, and
storage resource with them.  We propose a VM-centric approach that
simplifies deduplication and snapshot deletion.
The key advantage of this approach  is that while maintaining  a competitive deduplication efficiency,
the scheme requires little resource usage to minimize the impact on other collocated cloud services.
\comments{
The key contribution of this work is a set of methodologies to address the following two challenges:
1) simple deduplication and snapshot deletion with competitive efficiency and 
a small resource usage without affecting other collocated cloud services;
2) improved fault isolation for the sharing of deduplicated data,
given that node failures in converged architecture are the norm rather than
exception.
